Probabilistic Inference of Basic Stellar Parameters:\\ Application to Flickering Stars \altaffilmark{\titledag}

### 2015-06-02 version1.0/HBM.tex
ruth adds words

TBD

>>>>

We model the stochastic relationship between flicker, log($g$) and stellar
density, accounting for the fact that there exists some intrinsic scatter in
the dependent variable, and including the heteroskedastic uncertainties on both
the dependent and independent variables.
There are two excellent reasons for modelling the relation stochastically;
firstly, if the intrinsic scatter is ignored and the relation between
variables is assumed to be deterministic, those data points with smaller
measurement uncertainties may have an unrepresentative greater weighting
during the fitting process.
Secondly, we are interested in producing probability distributions over stellar
densities and surface gravities, as opposed to point estimates, and propagating
these probability distributions through to subsequent analyses.
Several recent studies have required posterior Probability Distribution
Function (PDF) samples, in order to conduct their (hierarchical)
analyses \citep[e.g.][]{Rogers2014, Foreman-Mackey2014, Angus2015}.
Including observational uncertainties on the independent variable within our
analysis is also important, because ordinary least squares regression methods
performed on data with two-dimensional uncertainties will result in a slope
that is biased towards zero
(e.g., Fuller 1987; Akritas \& Bershady 1996; Fox 1997).
or a demonstration of the effects of neglecting intrinsic scatter and
two-dimensional uncertainties, see Kelly (2007).

The two models describing the relationship between flicker, logg and stellar
density can be written as
\begin{equation}
	\log(g) \sim \mathcal{N}(\mu = \alpha + \beta F_8, \sigma^2 = \
	\sigma^2 + \gamma F_8)
\end{equation}
\label{eq:logg}
and
\begin{equation}
	\rho_* \sim \mathcal{N}(\mu = \delta + \epsilon F_8, \sigma^2 = \
	\sigma^2 + \zeta F_8),
\end{equation}
\label{eq:rho}
where $F_8$ is flicker and $\rho_*$ is stellar density.
The free parameters of the two models are $\alpha$, $\beta$, $\sigma_G$,
$\gamma$, $\delta$, $\epsilon$ and $\zeta$.
The two relationships can be described as Gaussian distributions with means
given by the equation of a straight line, and standard deviations given by
observational uncertainties, plus some dispersion which is a function of the
dependent variable.
